Three Problems for Sophistication

### 2015-01-20 Facticity/Facticity/paper.tex
plaatjes

\usepackage{amsmath,amsfonts}
\usepackage{color}
\usepackage[usenames,dvipsnames,svgnames,table]{xcolor}
\usepackage[mathscr]{eucal}
\usepackage{thmtools}

@@

>>>>

\usepackage{amsmath,amsfonts}
\usepackage{color}
\usepackage[usenames,dvipsnames,svgnames,table]{xcolor}
\usepackage[mathscr]{eucal}
\usepackage{thmtools}
\usepackage{graphicx}
\usepackage{caption}
\usepackage{subcaption}

@@

\begin{figure*}[tb]
  \hspace{-0.9cm}
  \begin{subfigure}[b]{0.55\textwidth}    
     \includegraphics[width=\textwidth]{./img/sophistication.pdf}
      \label{figure:sophistication}
  \end{subfigure}
  \begin{subfigure}[b]{0.55\textwidth} 
     \includegraphics[width=\textwidth]{./img/sophistication-jump.pdf}
      \label{figure:sophistication-jump}
  \end{subfigure}

  \caption{\small (left) A schematic representation of the idea of sophistication. We can represent the data $x$ in two parts: by describing first, a model, and then the residual information required to specify the data given the model. The smallest possible effective description, denoted by a black diagonal, is $C^\M(x)$. We accept all representation that come within a given \emph{slack} of this optimum, represented by a dashed line. The size of the smallest model within the slack is the sophistication of the data. (right) The same image, after a constant perturbation  in te model complexity caused by a change in numbering.}
  \label{fig:diagram}
\end{figure*}
